Preliminary Thesis Defence

### 2013-11-14 draft.Rnw
small fixes

\chapter{Replication of: Surviving Andersonville}

@@

Let us now suppose that our subject loses his wallet before the winner is drawn. If we want to predict how is beliefs have changed, we can for example assume that they are now 2below is mean belief. This would thus give us:

@@

If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to \emph{3s} above his mean level. Which would give us:

@@

Estimation of a 95\% confidence interval for a belief on probability, how the lottery profit from this.

>>>>

\chapter{Replication: Surviving Andersonville}

@@

Let us now suppose that our subject loses his wallet before the winner is drawn. If we want to predict how is beliefs have changed, we can for example assume that they are now one standard deviation below his mean belief. This would thus give us:

@@

If however, Janus there after is in a euphoric state because he find his wallet again, and on top of this a nice shiny green apple, than his new belief might change to 2 standard deviations above his mean level. Which would give us:

@@

Estimation of a 95\% confidence interval for a belief on probability, how the lottery profits from this.
